---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# lotterybr

<!-- badges: start -->
[![R-CMD-check](https://github.com/tomasbp2/lotterybr/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/tomasbp2/lotterybr/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of the package is to provide a function to automatically import data from the lotteries of Caixa Econômica Federal into the R environment. Data from the lotteries of Caixa Econômica Federal includes information on various games such as Mega-Sena, Lotofácil, Quina, among others. They are downloaded from the official website of the Federal Savings Bank at <https://loterias.caixa.gov.br/>.

## Installation

You can install the development version of lotterybr like so:

``` r
# install.packages("devtools")
# devtools::install_github("tomasbp2/lotterybr")
```

## Example

Downloading Lotofacil winners data:

```{r example, message = FALSE}

library(lotterybr)

lotofacil <- get_data(game= "lotofacil", type= "winners")

```
