---
title: "Lottery Brasil"
output: rmarkdown::html_vignette 
format: 
  html:
    toc: true
vignette: >
  %\VignetteIndexEntry{lotterybr}
  %\VignetteEngine{quarto::html}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(lotterybr)
```
This will open the shiny app for better visualisation of the datasets

# get_data

The function can be use in the following way

```{r}
quina_ganhadores = get_data(game ="quina",type = "winners","ptbr")
lotofacil_numbers = get_data(game = "lotofacil",type = "numbers","eng")
```

## Format

Each game has two datasets, numbers and winners, with the following columns:

### numbers
#### date

Date type, the date that the game occurred in.

#### course

Integer type, which course the game took place 

#### accumulated

Char type, if the game prize is accumulated "yes" or not "no"

#### numbers

Factor type with 60 levels, the drawn numbers.

### winners

#### date

Date type, the date that the game occurred in.

#### course

Integer type, which course the game took place .

#### accumulated

Char type, if the game prize is accumulated "yes" or not "no"

#### match

Char type, the possible match.

#### winners

Integer type, the number of winners of each possible match.

#### prize

Integer type, the prize for each type.

Some games, like "duplasena" or "diadesorte", may contain additional columns since each game has a different way of drawing numbers. Therefore, a brief explanation of each game is as follows.

### maismilionaria

Maismilionaria involves selecting five numbers from one pool and one additional number from another pool, with the potential to win multimillion-dollar jackpots.

### megasena

Six numbers are drawn from a pool of 60, with players aiming to match as many as possible for substantial prizes.

### lotofacil

Lotofacil involves picking 15 numbers from a pool of 25, with prizes awarded for varying levels of matches.

### quina

Players select five numbers from a pool of 80, aiming to match as many as possible for prizes.

### lotomania

Lotomania involves selecting 50 numbers from a pool of 100, with prizes awarded for matching a certain number of drawn numbers.

### duplasena

Dupla-Sena involves two separate draws, each with six numbers drawn from a pool of 50, offering double the chances to win.

### diadesorte

In Dia de Sorte, players choose seven numbers and a month, with prizes awarded for matching numbers and/or the month drawn.

## open_app

The function can be use in the following way

```{r}
#open_app(language = "eng")
```

it opens the shiny app containing a graph, table and a brief description of the selected game and data type. With the langugage argument, you can select either Portuguese or English.
You can view this app by clicking [Here](../articles/shinytest.html)
